\huge A Usability Evaluation of Tor Launcher

### 2017-03-03 pets2017-paper/pets2017-paper.tex
revision for shepherd

\begin{document}
   \author*[1]{Author 1}

  \author[2]{Author 2}

  \author[3]{Author 3}

  \author[4]{Author 4}

  \author[5]{Author 5}

  \author[6]{Author 6}

  \affil[1]{Affiliation of Author 1, E-mail: \mbox{author1@affiliation.edu}}
  \affil[2]{Affiliation of Author 2, E-mail: \mbox{author2@affiliation.edu}}
  \affil[3]{Affiliation of Author 3, E-mail: \mbox{author3@affiliation.edu}}
  \affil[4]{Affiliation of Author 4, E-mail: \mbox{author4@affiliation.edu}}
  \affil[5]{Affiliation of Author 5, E-mail: \mbox{author5@affiliation.edu}}
  \affil[6]{Affiliation of Author 6, E-mail: \mbox{author6@affiliation.edu}}
%  \author*[1]{Linda Lee}
%
%  \author[2]{David Fifield}
%
%  \author[3]{Nathan Malkin}
%
%  \author[4]{Ganesh Iyer}
%
%  \author[5]{Serge Egelman}
%  
%  \author[6]{David Wagner}
%
%  \affil[1]{University of California Berkeley, E-mail: \mbox{lnl@cs.berkeley.edu}}
%
%  \affil[2]{University of California Berkeley, E-mail: \mbox{fifield@cs.berkeley.edu}}
%
%  \affil[3]{University of California Berkeley, E-mail: \mbox{nmalkin@cs.berkeley.edu}}
%
%  \affil[4]{University of California Berkeley, E-mail: \mbox{ganesh.v@berkeley.edu}}
%  
%  \affil[5]{University of California Berkeley and International Computer Science Institute, E-mail: \mbox{egelman@cs.berkeley.edu}}
%   
%  \affil[6]{University of California Berkeley, E-mail: \mbox{daw@cs.berkeley.edu}}

@@

  \begin{abstract}
{
We perform the first usability test on Tor Launcher, a graphical user interface (GUI) that all Tor Browser users must use to configure their initial connection to the Tor network. Users who do not require a proxy or a non-default bridge can usually connect to the Tor network with the Tor Launcher GUI. However, user observations revealed that participants were intimidated by the tasks, unsure of what to do, and likely to get stuck configuring network components that they did not need. User testing showed that most users take more than 10 minutes to connect to Tor if the public relays are censored and half of the users cannot connect to Tor if the interface's hardcoded bridges are censored. We conclude with recommendations based on what we learned and start a discussion on alternative 
approaches to bootstrap a connection to Tor. 
}
\end{abstract}
  \keywords{Usable Security, User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

\section{Introduction}

Tor~\cite{dingledine2004tor} is an anonymity network that routes Internet traffic through a series of relays 
that make it difficult to observe the source and destination. 
Tor Browser~\cite{torbrowser} is a modified Firefox browser with a built-in Tor client that
is the recommended way to use Tor. Tor Launcher is a Tor Browser component that
starts, stops, and otherwise controls the underlying Tor processes.
Tor Launcher's graphical user interface (Figure~\ref{fig:old-interface}) asks the user to configure
bridges, pluggable transports, and proxies to make a connection to Tor (we refer to this graphical user interface as the ``configuration interface'' throughout this paper). This is the object of our study.

Although Tor Browser was originally designed for Internet anonymity, many now use Tor Browser to circumvent Internet censorship. In fact, many countries block Tor relays specifically to prevent their citizens from circumventing censorship~\cite{winter2012great}. The configuration interface mainly exists so that people who face Internet censorship can configure bridges, transports, and proxies to connect to Tor, but all Tor Browser users must interact with it regardless of why they use Tor Browser.

Tor minimizes collecting user data. Therefore, Tor does not have data on how users interact with the configuration interface. While we agree that this is respectful to the users, we also believe that this data will be helpful to improve the usability of the configuration interface. Improving the usability of the configuration interface has the obvious benefit of helping more users connect to Tor. But this is also benefits the Tor Project (less help desk tickets) and other Tor users (an increase in overall users increases the anonymity set~\cite{dingledine2006anonymity}).

We started our usability evaluation by inspecting the interface (section~\ref{sec:inspection}) and
running observing participants interact with it (section~\ref{sec:qualitative}). 
We opportunistically used the insights from our observations to make some changes (section~\ref{sec:design}).
Then we quantified how usable the interface was, and 
how much our changes helped save users time (section~\ref{sec:quantitative}).
Afterward, we gave some recommendations (section~\ref{sec:recommendations}), addressed
limitations of our evaluation (section~\ref{sec:limitations}), and framed our work in the context of existing work (section~\ref{sec:related}). \\

\noindent This paper contributes:
\smallskip
\begin{itemize}
\item an inspection of the Tor Launcher 5.0.3 interface
\item what users found challenging about the interface
\item measurements of how many users could connect
\item measurements of how long users took to connect
\item patterns seen in the users that failed to connect
\item recommendations to improve the interface
\end{itemize}

We hope that our work contributes to Tor Browser and is an informative case study of users interacting with anonymity and censorship circumvention tools.

\section{Technical Background}
\label{sec:background}
This section discusses network components, when to configure them, and how they connect to Tor.

@@

In this paper, the word ``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy. This is to maintain consistency with the wording in the configuration interface. Fig.~\ref{fig:topology} illustrates the interacting components. A proxy is technically an intermediary between clients and servers, so a single Tor relay, a bridge, the circuit of entry, middle, and guard relays, and local proxies can all can be considered a proxy. A user uses a proxy to bypass local firewalls.

Tor relays are the routers in the Tor network. The Tor network is a group of routers that perform onion routing, a technique for anonymous communication over a computer network.  
Guard relays serve as an entry node into the Tor network and receive packets from the user. Middle relays forward traffic from an entry relay to an exit relay, and provide an extra layer of encryption in the Tor network. Exit relays receive traffic from a middle relay, and direct the traffic to its intended destination. 
A user uses Tor Browser to connect to the Tor network, which indirectly connects to websites.

Bridges are unlisted Tor relays that serve as an alternative entry node.
Bridges can be unlisted relays that behave similarly to a regular Tor relay,  
but most run a pluggable transport (referred to as ``transport'' for shorthand) that obfuscates traffic. 
Pre-configured bridges can be selected by ``Transport type,'' which refer to various
censorship circumvention technologies (``pluggable transports'').
Most transports rely on the secrecy of their static IP addresses for their effectiveness.
These include ``fte'' and ``fte-ipv6''~\cite{fte},
which disguise the Tor protocol as another protocol (such as HTTP), and
``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
which encrypt or alter the Tor protocol to appear as random noise.
Other transports route traffic through other services and do not need a secret IP address. 
``flashproxy''~\cite{flashproxy} connects through third party web browsers,
and the ``meek''~\cite{fifield2015blocking} options route traffic
through content delivery networks. Fig.~\ref{fig:old-bridge-combobox} shows the bridge and transport options at the time of the study. A user uses a bridge to connect to the Tor network while Tor relays or the Tor network protocol is being censored.

\subsection{State and Corporate Censorship}
A local proxy is required to connect in certain managed networks (i.e. universities and corporations). This usually means that users cannot connect to the Internet at all without a proxy, including connecting to the Internet through Tor. The user must first successfully connect to the Internet through their proxy before trying to connect to a Tor relay or bridge.

State level censors block access to the Tor network by blocking publicly listed Tor relays. Some also employ more sophisticated techniques such as deep packet inspection and protocol detection. This means that users can connect directly to (uncensored) websites, but Tor is blocked. The thoroughness of censorship is what requires different bridges and transports.

@@

\subsection{Connecting to Tor} 
A ``bridge line,'' a specifically formatted bridge specification that
includes its IP address, transport type, and other metadata 
officially configures Tor Browser to use bridges.
Users can do this more easily by choosing
a hard-coded option in the interface (see Figure~\ref{fig:old-bridge-combobox}) 
that select a group of bridges that use a particular transport.
For instance, choosing the hard-coded obfs3 option
configures a handful of bridges that use the obfs3 transport.
If the built-in bridges do not work, users can obtain bridge lines
through out-of-band channels~\cite{bridgedb}.

Configuring a proxy requires providing the proxy protocol, IP address, port, and additional optional fields. The user must locate and input this information. If the computer is already configured to use a proxy, the information can be found in other browsers. The interface tells users to ``check Internet settings in another browser'' if they are unsure of the proxy information.

There are many valid configuration settings to connect to the Tor network.
A user who does not need a bridge or proxy can connect with a bridge, proxy, or both, provided that they are configured correctly.

\begin{figure*}
\centering
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-first.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The first screen (F). ``Connect'' connects directly to a public Tor relay unless bridges or proxies are configured.``Configure'' leads to the first bridge screen (Figure~\ref{fig:old-bridge}). }
	\label{fig:old-first}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridges.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The first bridge screen (B1). Answering yes directs users to a screen to configure bridges (Figure~\ref{fig:old-bridge-settings}). Answering no directs users to the proxy question screen (Figure~\ref{fig:old-proxy}).}
	\label{fig:old-bridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The second bridge screen (B2). Users select a provided bridge or a custom one (bridges not hard coded into the interface). ``Help'' directs to bridge help screen (Figure ~\ref{fig:old-bridge-help}). }
	\label{fig:old-bridge-settings}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings-combobox.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The hardcoded bridges are listed alphabetically by the transport that they support. Each transport works differently, but their functions are not explained in the interface.}
	\label{fig:old-bridge-combobox}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeHelp.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The bridge help screen (BH) gives instructions for a custom bridge three different ways. ``Done'' redirects users back to the second bridge screen (Figure~\ref{fig:old-bridge-settings}).}
	\label{fig:old-bridge-help}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-proxy.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The first proxy screen (P1). Answering yes to this question directs to the proxy settings screen (Figure ~\ref{fig:old-proxy-yes}). Answering no starts a connection to Tor.}
	\label{fig:old-proxy}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-proxyYES.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The proxy settings screen (P2). Users configure a proxy by filling in the proxy's protocol, IP address, and port. ``Connect'' starts a connection to Tor with the interface settings.}
	\label{fig:old-proxy-yes}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-progress.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The progress bar (Pr). The bar fills up as log messages update the connection status. Warnings do not interrupt this bar but an error replaces this window with an alert. }
	\label{fig:old-progress}
\end{subfigure}
\caption{
The Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:old-interface}
\end{figure*}

\section{Methodology} 
This section discusses how we performed our summative evaluation to determine the interface's effectiveness.

\subsection{Testing Pipeline} 
We performed a cognitive walkthrough~\cite{cognitive-walkthrough} of the interface by working tasks from the perspective of the user and assessing its learnability for new or infrequent users.

We then conducted qualitative and quantitative usability tests of the interface. We believed that both were necessary for a complete evaluation. Qualitative testing tells you {\it why or how} it is or is not usable, while quantitative testing tells you {\it how much} it is or is not usable. Five users is considered to be the maximum benefit-cost ratio for gaining insights~\cite{howmanyusers}, so we recruited five participants for each condition in our qualitative experiment. Twenty users is considered to be the minimum for statistically significant measurements~\cite{howmanyusers}, so we recruited twenty participants for each condition in our quantitative experiment.

We opportunistically used our observations from the qualitative study to design interface changes that would address common issues that our participants encountered. We also opportunistically used our quantitative testing setup to measure its usability with respect to the original interface. We found the process of identifying design principles, drafting design changes, and testing an alternative interface to be insightful and hope that this may be insightful to others as well.

\subsection{Evaluation Metrics}
\label{sec:eval}
Usability measures users' abilities to complete tasks. We use the following industry-standard~\cite{albert2013measuring} metrics: \\

\begin{itemize}
\item {\bfseries Completion rate:}  percentage of users that connect to Tor in an experimental condition. 
\item {\bfseries Connection time:} time from Tor Browser startup to a successful connection to Tor. 
\item {\bfseries Configuration time:} time users spent in Tor Launcher configuring bridges and proxies, not counting time spent passively waiting.
\end{itemize}

Completion rate is the fundamental usability metric that measures if users can accomplish the task. We defined success as a binary metric that is true if a user connected to Tor and false if a user did not.

Task time is a supplemental usability metric that measures user productivity during the task. We measured this in two ways. Connection time measures how long users took to connect to Tor, which includes time spent waiting for Tor to configure relays for the user. This can take up to a couple minutes and dominate the measurement. Configuration time measures the time users spent configuring bridges and proxies.

\subsection{Experimental Setup}
\label{sec:environments}
We use versions of Tor Browser~5.0.3, 
the most recent stable release at the time~\cite{torbrowser-503}.
There were new releases during the experiments, but
we used the same version throughout to not introduce
confounding factors.

We simulated three environments of increasing severity in censorship (E1, E2, E3).
Table~\ref{tab:environments} summarizes them and explains what is required to connect to Tor. We chose to 
simulate environments for the stability and reproducibility of the 
experiment, as real censored networks are volatile and complex.

@@

The simulated environments are not intended to imitate any particular country's censorship environment. Rather, they were designed to require particular network configurations
to connect to Tor. We believe this to be sufficient for the purpose of testing the configuration interface, since these environments require the user to take the interface paths we wanted to test.

We conducted our studies at <redacted>, which only had Windows machines. 
So we used Windows Firewall rules to block the IP addresses of public Tor relays (E2, E3) and default bridges (E3),
and the Windows operating system hosts file to block websites by
mapping domain names to localhost (127.0.0.1) (E1, E2, E3). For all experiments, we blocked torproject.org and its subdomains to discourage downloading Tor Browser (as we had installed a specific version on the test computers) and wikipedia.org, cnn.com, and their subdomains (these were our simulated ``censored'' websites).

\section{Usability Inspection}
\label{sec:inspection}
This section discusses our inspection of the configuration interface and the resulting observations.

\subsection{Procedure} 
Two researchers performed the cognitive walkthrough on the Tor Browser 5.0.3 Tor Launcher GUI, the most recent version deployed at the time (Figure~\ref{fig:old-interface}). We systematically tried actions from the perspective of a typical user, which we defined as a first time or infrequent user with almost no previous knowledge about network components involved in connecting to Tor.

We first examined each screen in the interface for tasks required, inputs taken, and consequences of possible actions. This was done to map all potential paths through the interface (Figure~\ref{fig:digraph}). We then stepped through each user path and recorded our observations.

\subsection{Observations}
The interface did not suppose that a user has previous exposure to Tor. To help new users, it provided recommendations in the text and populated some options (such as bridges) with recommended options. However, the interface did require the user to figure out if Tor relays are blocked or if a proxy is required. And the interface did not discourage users from configuring components that are not necessary to connect to Tor. The proxy configuration has the potential for a lot of error, as there are many free-form input fields.

More generally, we suspected that new users or infrequent users would struggle to configure bridges and proxies. We doubted that users would understand the Internet well enough to even explain how Tor relays, bridges, and proxies worked. Additionally, as mentioned previously, Tor relays, bridges, and proxies all allow indirect connections, and the difference in terminology can be confusing. The terminology of bridges and transports are also specific to Tor, and not other censorship circumvention software.

We used the map of potential user paths (Figure~\ref{fig:digraph}) to design our simulated environments (section~\ref{sec:environments}).  We used our walkthrough observations as inspiration for drafting our post-experiment interview questions (Appendix~\ref{interview-questions}) for qualitative usability testing.

@@

\section{Qualitative Testing}
\label{sec:qualitative}
This section discusses our small-scale, qualitative usability experiment and resulting user insights.

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked a prescreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} so that we could have a diversity of gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% identified as male and 50\% identified as female. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). One participant declined to report their age, so age calculations omit this participant's information. All of our users were highly educated, having at least some college education. We verified their self-reported familiarity with Tor Browser in-person to identify new users, and found that 12 were new users and 4 had previously used Tor Browser in some capacity.

@@

We distributed participants evenly in number across experimental conditions:  5~in E1, 5~in E2, and 6~in E3. We ensured that each condition had a participant who had used Tor Browser before, and tried for some variation in gender, age, ``technical expertise,'' and ``use of security tools'' in each experimental condition as well.

\subsection{Setup} 
We ran the experiment in a meeting room in <redacted building> at <redacted university>. The room had a desk and chair, where a monitor, keyboard, and a Windows computer were set up. On a clean computer, we manually downloaded and installed the necessary software for the experiment: Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in another browser of their choice, and VLC to record the screen during the experiment. Before each participant entered the room, we ran a script on the computer that
set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.

\subsection{Procedure}
Three researchers ran the qualitative user tests. Each session had at least two researchers.  
We told the participant the purpose of the 
study, what data was collected, and any associated risks. 
Then they signed a consent form with this information in writing. 
Before the experiment, we clarified that they could stop at any time during the experiment with no negative consequences.

We started by informing the participant of the simulated censorship environment (Appendix~\ref{qualitative-script}) and task. We explicitly stated that they should use Tor to circumvent censorship. 
We instructed them to visit sample censored and uncensored websites
in a non-Tor browser to clarify that the Internet was functioning and
pointed out the Tor Browser shortcut on their desktop.

They were asked to complete a worksheet (Appendix~\ref{participant-worksheet}) that 
required answers from Wikipedia (censored) and CNN (uncensored).
We chose these websites because their likely familiarity~\cite{alexa}
would make the task seem less intimidating. They were given 45 minutes to complete the task. 
After instructions, researchers left to minimize interactions and watched a live feed of the participants' screen from another room.

>>>>

\begin{document}
  \author*[1]{Linda Lee}

  \author[2]{David Fifield}

  \author[3]{Nathan Malkin}

  \author[4]{Ganesh Iyer}

  \author[5]{Serge Egelman}

  \author[6]{David Wagner}

  \affil[1]{University of California Berkeley, E-mail: \mbox{lnl@cs.berkeley.edu}}

  \affil[2]{University of California Berkeley, E-mail: \mbox{fifield@cs.berkeley.edu}}

  \affil[3]{University of California Berkeley, E-mail: \mbox{nmalkin@cs.berkeley.edu}}

  \affil[4]{University of California Berkeley, E-mail: \mbox{ganesh.v@berkeley.edu}}

  \affil[5]{University of California Berkeley and International Computer Science Institute, E-mail: \mbox{egelman@cs.berkeley.edu}}

  \affil[6]{University of California Berkeley, E-mail: \mbox{daw@cs.berkeley.edu}}

@@

  \begin{abstract}
{
Although Tor has state-of-the art anti-censorship measures, users in heavily censored environments will likely not be able to connect to Tor because they cannot make the correct decisions during the configuration process. We perform the first usability evaluation of Tor Launcher, the graphical user interface (GUI) that Tor Browser uses to configure their connections to Tor. Our study shows that 79\% (363 of 458) of user attempts to connect to Tor failed, and found that users were often frustrated during the process and try options at random. In this paper, we describe how we measured potential usability issues, discuss design constraints unique to Tor, and provide recommendations based on what we learned to help more users connect to Tor while reducing the time they take to do so. Tor Browser ~4.5 incorporated  changes based on our work.
}
\end{abstract}
  \keywords{Usable Security, User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

\section{Introduction}
Tor~\cite{dingledine2004tor} is an anonymity network that routes Internet traffic through a series of relays 
that make it difficult to observe the source and destination.  Tor Browser~\cite{torbrowser} is a modified Firefox browser that routes traffic through Tor. Tor Launcher is a Tor Browser graphical user interface (Figure~\ref{fig:old-interface}) that asks the user to configure their connection to Tor. This is the object of our study.

Although Tor Browser was originally designed for Internet anonymity, many now use Tor Browser to circumvent Internet censorship. Many countries block Tor relays specifically to prevent their citizens from circumventing censorship~\cite{winter2012great}. The configuration interface mainly exists so that people who face Internet censorship can configure bridges, transports, and proxies to connect to Tor. Improving Tor launcher has the obvious benefit of helping censored users connect to Tor, but this is also benefits other Tor users by increasing in overall users increases the anonymity set~\cite{dingledine2006anonymity}).

We started our usability evaluation by inspecting the interface (section~\ref{sec:inspection}) and
running observing participants interact with it (section~\ref{sec:qualitative}). 
We used the insights from our observations to make some changes to the interface (section~\ref{sec:design}) and
quantified how usable the interface was before and after changes (section~\ref{sec:quantitative}).
Afterward, we gave recommendations based on what we learned (section~\ref{sec:recommendations}), addressed
limitations of our evaluation (section~\ref{sec:limitations}), and framed our work in the context of existing work (section~\ref{sec:related}). We hope that our usability evaluation serves as an informative case study and provides guidance on improving Tor launcher.

\section{Technical Background}
\label{sec:background}
This section discusses how to connect to Tor and what network components are involved.

@@

Technically, proxies are any computer or service that allow its users to make indirect network connections to other services. In this sense, any Tor relay and the Tor circuit can also be considered to be a proxy. However, in this paper and verbally, the word ``proxy'' refers to a SOCKS or HTTP proxy that bypasses local firewalls. Fig.~\ref{fig:topology} illustrates the network components involved.

Tor relays are the routers in the Tor network. The Tor network is a group of routers that perform onion routing, a technique for anonymous communication over a computer network.  Guard relays receive packets from the user and forward traffic to middle relays. Middle relays forward traffic from an entry relay to an exit relay. Exit relays receive traffic from a middle relay and direct the traffic to its intended destination.  A user uses Tor Browser to connect to the Tor network, which connects to websites on behalf of the user.

Bridges are unlisted alternative entry nodes used to connect to Tor when Tor relays are censored.
Bridges also recieve packets from the user and forward traffic to middle relays, but also run a pluggable transport (referred to as ``transport'' for shorthand). Bridges are grouped by which transport they run for convenience.

Most bridges can be blocked by blocking their static IP addresses. These include bridges that run``fte'' and ``fte-ipv6''~\cite{fte} transports, which disguise the Tor protocol as another protocol (such as HTTP), and ``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit} transports, which encrypt or alter the Tor protocol to appear as random noise. Other bridges are less blockable because of how they work. Bridges that run the ``flashproxy''~\cite{flashproxy} and ``meek''~\cite{fifield2015blocking} transports route traffic through third party web browsers and content delivery networks. What bridges are accesssible in each country varies. Fig.~\ref{fig:old-bridge-combobox} shows the bridge and transport options at the time of the study.

@@

\subsection{Connecting to Tor} 
There are many valid configuration settings to connect to the Tor network.
A user who does not need a bridge or proxy can connect with a bridge, proxy, or both, provided that they are configured correctly.

Users can configure a bridge by choosing a transport (Figure~\ref{fig:old-bridge-combobox}), which selects the group of bridges that use that transport. If the built-in bridges do not work, users can obtain bridge lines through out-of-band channels~\cite{bridgedb} that provides the necessary bridge specifications. Configuring a proxy requires entering in the proxy protocol, IP address, port, and additional optional fields (Figure~\ref{fig:old-proxy}). The user must locate this information.

\begin{figure*}
\centering
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-first.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The first screen (F). ``Connect'' starts a connection.``Configure'' leads to the first bridge screen (Figure~\ref{fig:old-bridge}). }
	\label{fig:old-first}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridges.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The first bridge screen (B1). ``Yes'' leads to a bridge configuration screen (Figure~\ref{fig:old-bridge-settings}) and ``no'' skips it.}
	\label{fig:old-bridge}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The second bridge screen (B2). Users select a bridge here. ``Help'' directs to bridge help screen (Figure ~\ref{fig:old-bridge-help}). }
	\label{fig:old-bridge-settings}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings-combobox.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{Some hardcoded bridges are listed alphabetically by their transport. The recommended one is obfs3.}
	\label{fig:old-bridge-combobox}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeHelp.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The bridge help screen (BH) talks about getting a custom bridge. ``Done'' leads back to the previous screen.}
	\label{fig:old-bridge-help}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-proxy.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The proxy question screen (P1). ``Yes'' goes to the proxy settings screen (Figure ~\ref{fig:old-proxy-yes}). and ``no'' starts a connection.}
	\label{fig:old-proxy}
\end{subfigure}
~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-proxyYES.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The proxy settings screen (P2). ``Connect'' starts a connection to Tor with the interface settings.}
	\label{fig:old-proxy-yes}
\end{subfigure}
~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{subfigure}[b]{0.30\textwidth}
	\includegraphics[width=\textwidth]{screenshots/OLD-progress.png}
	\centering\captionsetup{width=1.5\linewidth}%
	\caption{The progress bar (Pr). The bar fills up as log messages update the connection status. }
	\label{fig:old-progress}
\end{subfigure}
\caption{
The Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
}
\label{fig:old-interface}
\end{figure*}

\section{Methodology} 
This section discusses the process we used to determine the usability of Tor launcher interface.

\subsection{Testing Pipeline} 
We inspected the interface to anticipate potential problems and formally assess its pros and cons. We then conducted qualitative and quantitative usability tests. We believed both were necessary for a complete evaluation. Qualitative testing tells you {\it why or how} it is or is not usable, while quantitative testing tells you {\it how much} it is or is not usable. Five users is considered to be the maximum benefit-cost ratio for gaining insights~\cite{howmanyusers}, so we recruited five participants for each condition in our qualitative experiment. Twenty users is considered to be the minimum for statistically significant measurements~\cite{howmanyusers}, so we recruited twenty participants for each condition in our quantitative experiment.

We opportunistically used our observations from the qualitative study to design interface changes that would address common issues that our participants encountered. We also opportunistically used our quantitative testing setup to measure its usability with respect to the original interface. We discuss how our changes saved users time and recommend some changes.

\subsection{Evaluation Metrics}
\label{sec:eval}
We use the following industry-standard~\cite{albert2013measuring} metrics to determine if the launcher is usable: \\

\begin{itemize}
\item {\bfseries Completion rate:}  percentage of users that connect to Tor. A high completion rate is ideal. 
\item {\bfseries Connection time:} time until a successful connection to Tor. This should be a couple minutes. 
\item {\bfseries Configuration time:} time users spent in Tor Launcher configuring bridges and proxies, which excludes time waiting for connections to establish or timeout. This should be as short as possible.
\end{itemize}

Completion rate is the fundamental usability metric that measures if users can accomplish the task. We defined success as a binary metric that is true if a user connected to Tor and false if a user did not. Task time is a supplemental usability metric that measures user productivity during the task. We measured this in two ways. Connection time measures how long users took to connect to Tor, which includes the time Tor takes to establish a series of relays. Since that time can dominate the measurement, we use configuration time to measure the time users spent configuring bridges and proxies.

\subsection{Experimental Setup}
\label{sec:environments}
We simulated three environments of various censorship severity (Table~\ref{tab:environments}). We chose to 
simulate environments for the stability and reproducibility of the experiment, as real censored networks are volatile and complex.

@@

The simulated environments are not intended to imitate any particular country's network. Rather, they were designed to require different bridges to connect to Tor. We believe this to be sufficient for the purpose of testing the configuration interface, since this requires the user to take the interface paths we wanted to test.

We used Tor Browser~5.0.3, the most recent stable release at the time~\cite{torbrowser-503}.
There were new releases during the experiments, but we used the same version throughout to not introduce confounding factors.

We conducted our experiments on Windows machines. To create the environments, we used Windows Firewall rules to block the IP addresses of public Tor relays and default bridges, and the Windows hosts file to block websites by mapping domain names to localhost.

\section{Usability Inspection}
\label{sec:inspection}
We inspected of the interface to anticipate potential problems before testing it on users.

\subsection{Procedure} 
Two researchers performed the cognitive walkthrough~\cite{cognitive-walkthrough} on the Tor Browser 5.0.3 Tor Launcher GUI, which was the most recent version deployed at the time (Figure~\ref{fig:old-interface}). We first examined each screen in the interface for tasks required, inputs taken, and consequences of possible actions. This was done to map all potential paths through the interface (Figure~\ref{fig:digraph}). We then stepped through each user path, systematically tried all possible actions, and recorded our observations.

\subsection{Observations}
We noticed that the interface leaves a lot of freedom for error but does not give good instructions on when there is an error and how to fix it: \\

\begin{itemize}
\item {\bfseries Difficult tasks:} The interface uses technical and Tor-specific terms that are unfamiliar to an average user, such as the Tor network, internet service provider (ISP), local proxy, bridges, and transports. 
\item {\bfseries Too many choices:}  Users who do not need a bridge or proxy are able to configure them. There are nine choices for bridges by transport and more options to input a custom bridge. Almost any HTTP or SOCKS proxy can be used as the proxy. Custom bridge lines require the bridge information with specific syntax, but this syntax is not specified in the interface. Proxy fields also do not provide syntactic guidlines. See the whole list of possible errors in Appendix~\ref{states}. 
\item {\bfseries Poor feedback:} Even if there was a syntactic error in your bridge or proxy fields, it does not notifiy until a connection is made and fails. If a censored bridge was chosen, the connection timeout takes a over a couple minutes. Errors messages were often technical and did not give suggestions.
\end{itemize}

These are some of the factors that contributed to why users struggled with the interface and therefore were unable to connect to Tor quickly.

@@

\section{Qualitative Testing}
\label{sec:qualitative}
We observed user behaviors to see why Tor is hard to use and interviewed users afterward to see how they felt.

\subsection{Recruitment}
We recruited people from Craigslist using an ad (Appendix~\ref{qualitative-recruitment}) and prescreening survey (Appendix~\ref{qualitative-prescreening}). We pre-screened~\cite{screening} so that we could have a diversity of gender, age, and familiarity with Tor in a small participant pool. Of our 16 recruited participants, 50\% identified as male and 50\% identified as female. Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$). One participant declined to report their age, so age calculations omit this participant's information. All of our users had at least some college education. 12 were new users and 4 had previously used Tor Browser in some capacity.

@@

We distributed participants evenly across experimental conditions:  5~in E1, 5~in E2, and 6~in E3. We ensured that each condition had new and previous Tor Browser users, and tried for variation in gender and age.

\subsection{Procedure} 
We ran the experiment in a meeting room at UC Berkeley. The room had a desk and chair, where a monitor, keyboard, and a Windows computer were set up. On a clean computer, we downloaded and installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in another browser of their choice, and VLC to record the screen during the experiment. Before each participant, we ran a script on the computer that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.

Each one-hour session was run by at least two researchers. We started by informing the participant of the study, task, and risks (Appendix~\ref{qualitative-script}). After they consent to the experiment, we instructed them to visit sample censored and uncensored websites in a non-Tor browser to illustrate that some sites are blocked. We explicitly tell them to use Tor to circumvent censorship. The worksheet (Appendix~\ref{participant-worksheet}) required answers from a censored website (Wikipedia) and an uncensored website (CNN). We chose Wikipedia and CNN because they were popular websites~\cite{alexa} and their likely familiarity would make the task seem less intimidating. After instructions, researchers gave left the room to minimize interactions and watched a live feed of the participants' screen.

After 45 minutes (or when they finished the worksheet), we interviewed them. We asked both general questions (Appendix~\ref{interview-questions}) and additional participant-specific questions that verified our observations (e.g. ``the participant was selecting bridges at random''). We gave them~\$30 for their time.
